Poster figures

### 2025-02-27 analysis/poster_ncar/presentation_figures.Rmd
Tweaks

topo_inset <- list(topo_lonlat) |>
  rep(4) |>
  rbindlist(idcol = "month") |>
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = z),
                    breaks = c(0, Inf), fill = "gray90") +
  geom_contour2(aes(z = z),
                breaks = 0) +
  facet_wrap(~month, labeller = labeller(mohth = rep("", 4)), nrow = 1) +
  scale_y_latitude(limits = c(-90, -60)) +
  scale_x_longitude(ticks = 60, expand = c(0.08, 0)) +
  theme_void() +
  theme(strip.background = element_blank(),
        strip.text = element_blank(),
        aspect.ratio = 0.1,
        plot.margin = margin(c(-50, 0, 0, 0)))

theme_margin <- theme_get()$plot.margin
theme_margin[3] <- margin(-10)[1]

@@

  scale_y_continuous(breaks = NULL, expand = c(0, 0)) +
  labs(fill = NULL, 
       y = "Lead time") +
  wide_legend +
  facet_wrap(~ month, labeller = labeller(month = labels_month)) +
  theme(panel.background = element_blank(), 
        tagger.panel.tag.background = element_rect(colour = "white", fill = "white"), 
        plot.margin = theme_margin) +
  tag_facets(position = list(x = 0.08, y = 1, hjust = 0, vjust = 1)) +

>>>>

topo_inset <- list(topo_lonlat) |>
  rep(4) |>
  rbindlist(idcol = "month") |>
  ggplot(aes(lon, lat)) +
  geom_contour_fill(aes(z = z),
                    breaks = c(0, Inf), fill = "gray90") +
  geom_contour2(aes(z = z),
                breaks = 0) +
  facet_wrap(~month, labeller = labeller(mohth = rep("", 4)), nrow = 1) +
  scale_y_latitude(limits = c(-90, -60)) +
  scale_x_longitude(ticks = 60, expand = c(0.08, 0)) +
  theme_void() +
  theme(strip.background = element_blank(),
        strip.text = element_blank(),
        aspect.ratio = 0.1)

@@

  scale_y_continuous(breaks = NULL, expand = c(0, 0)) +
  labs(fill = NULL, 
       y = "Lead time") +
  wide_legend +
  facet_wrap(~ month, labeller = labeller(month = labels_month)) +
  theme(panel.background = element_blank(), 
        tagger.panel.tag.background = element_rect(colour = "white", fill = "white")) +
  tag_facets(position = list(x = 0.08, y = 1, hjust = 0, vjust = 1)) +
  coord_cartesian(clip = "off") +
